My title

### 2024-11-04 paper/paper.qmd
big update for model and results

## Measurement/ Data Visualization

@@

```{r, fig.height= 3}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportstate
#| fig-cap: "Distribution of Support Percentage by State"

@@

harrisdata <- harrisdata %>%
  mutate(
    end_date_num = as.numeric(end_date - min(end_date)),
        state = factor(state))

@@

combined_data <- harrisdata %>%
  inner_join(trumpdata, by = c("state", "pollster", "sample_size", "end_date")) %>%
  mutate(
    harris_percentage = (num_harris / sample_size) * 100,
    trump_percentage = (num_trump / sample_size) * 100
  )

@@

# Plotting the support percentages side-by-side for each state
plot_data <- combined_data %>%
  pivot_longer(cols = c(harris_percentage, trump_percentage),
               names_to = "candidate",
               values_to = "support_percentage") %>%
  mutate(candidate = ifelse(candidate == "harris_percentage", "Harris", "Trump"))

# Plotting the support percentages side-by-side for each state
ggplot(plot_data, aes(x = state, y = support_percentage, fill = candidate)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  labs(,
    x = "State",
    y = "Support Percentage"
  ) +
  scale_fill_manual(values = c("Harris" = "blue", "Trump" = "red"), name = "Candidate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1, size = 8))
```

@@

```{r, fig.height= 4, fig.width= 6}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportharris
#| fig-cap:  "Support Percentage for Harris by State"

@@

# Plot showing the variation in Harris's support percentages by pollster within each state
ggplot(harrisdata, aes(x = state, y = pct)) +
  geom_boxplot(aes(fill = state), alpha = 0.6, outlier.shape = NA) +  # Boxplot to show spread by pollster within each state
  geom_jitter(aes(color = state), width = 0.2, alpha = 0.4) +  # Adds individual points with jitter to show individual poll results
  labs(
    x = "State",
    y = "Support Percentage"
  ) +
  theme_minimal() +
  theme(legend.position = "none") 
```

@@

```{r, fig.width= 6, fig.height= 3}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportWP
#| fig-cap:  "Support Percentage for Harris by State since Harris declared as Candidate for Wisconsin and Pennsylvania"

# Filter for a subset of states to plot separately
subset1 <- harrisdata %>% filter(state %in% c("Wisconsin", "Pennsylvania"))

# Plot the first subset
ggplot(subset1, aes(x = end_date, y = pct, color = state)) +
  geom_point() +
  geom_smooth(se = TRUE) +
  facet_wrap(~ state, scales = "free_y") +
  labs(y = "Harris Percent", x = "Date") +
  theme_minimal() +
    scale_x_date(
    date_breaks = "1 month",            # Set major breaks at monthly intervals
    date_minor_breaks = "1 week",       # Optional: add minor weekly breaks for granularity
    date_labels = "%b %d"               # Format to show abbreviated month and day (e.g., "Aug 01")
  ) +
   theme(legend.position = "none")

```
In @fig-supportWP, Pennsylvania and Wisconsin display distinct trends. In Pennsylvania, support for Harris has been relatively consistent since early September, stabilizing around 48.5%. In contrast, Wisconsin shows a peak in support in mid-September, followed by a gradual decline that stabilizes in October. These observations suggest that while Pennsylvania remains a consistent stronghold for Harris, Wisconsin’s voter sentiment may be more susceptible to fluctuations.

```{r, fig.width= 6, fig.height= 3}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportAM
#| fig-cap:  "Support Percentage for Harris by State since Harris declared as Candidate"

@@

```{r, fig.width= 7, fig.height= 3}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportGNN
#| fig-cap:  "Support Percentage for Harris by State since Harris declared as Candidate"

@@

# Plot the first subset
ggplot(subset3, aes(x = end_date, y = pct, color = state)) +
  geom_point() +
  geom_smooth(se = TRUE) +
  facet_wrap(~ state, scales = "free_y") +
  labs(y = "Harris Percent", x = "Date") +
  theme_minimal() +
        scale_x_date(
    date_breaks = "1 month",
    date_minor_breaks = "1 week",
    date_labels = "%b %d" 
  ) +
   theme(legend.position = "none")
```
In @fig-supportGNN, we analyze Georgia, Nevada, and North Carolina. Nevada demonstrates the highest variability in Harris's support, which could reflect the state’s dynamic political response to recent campaign efforts. Georgia shows a steady upward trend, indicating growing support for Harris, while North Carolina reveals a slight decline since October, suggesting a possible shift in voter support.

```{r, fig.width= 6, fig.height= 3}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportpollsters
#| fig-cap: "Variation in Harris's Support Percentage Across Pollsters Over Time"

@@

ggplot() +
  # Draw a line for each pollster from first to last poll
  geom_line(data = harrisdata %>% group_by(pollster) %>% filter(n() > 1), 
            aes(x = end_date_num, y = pct, group = pollster, color = pollster), 
            alpha = 0.1) +
  # Draw points for each poll (including those with only one poll)
  geom_point(data = harrisdata, aes(x = end_date_num, y = pct, color = pollster), 
             size = 0.5, alpha = 0.3) +
  # Add the median line with ribbon for variability
  geom_line(data = pollster_summary, aes(x = end_date_num, y = median_support), 
            color = "blue", size = 1) +
  geom_ribbon(data = pollster_summary, aes(x = end_date_num, ymin = lower_quartile, ymax = upper_quartile), 
              fill = "lightblue", alpha = 0.2) +
  labs(
    x = "Days Since Declaration",
    y = "Support Percentage"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

```
In @fig-supportpollsters, we examine the impact of pollster variability on Harris's support percentage over time. This visualization introduces the variable pollster, highlighting the differences in polling results that arise from varying methodologies. The chart reveals considerable fluctuations and occasional outliers in Harris' support, likely due to the distinct approaches each pollster employs in sampling and weighting responses.

@@

To introduce the outcome and predictor variables effectively, you’ll want to set the stage for your model by clearly defining what you are trying to predict (the outcome variable) and the factors that you believe influence it (the predictor variables). This section should provide context on why each variable is included and how it might impact the results, without yet delving into the specific mechanics of the model itself.

Here’s an example of how to structure this paragraph:

@@

1. State: Since support for candidates can vary significantly across different states due to regional demographics, political history, and local issues, the state variable allows us to capture these geographical differences. As shown in the earlier visualizations, some states demonstrate consistently higher or lower support for Harris, emphasizing the importance of including state-level distinctions in our analysis.

2. Days Since Declaration: Representing the number of days since Harris declared her candidacy, this temporal variable helps us capture shifts in voter sentiment over time. Our analysis reveals several critical points where support trends noticeably change, such as the upward or downward shifts in mid-September. This predictor allows the model to account for these temporal patterns and track how Harris’s support evolves as the campaign progresses.

3. Pollster: Given that different pollsters employ varied methodologies, sampling techniques, and weighting schemes, the pollster variable captures the potential variability introduced by each polling organization. As illustrated in @fig-supportpollsters, the results can vary considerably depending on the pollster, with some reporting notably higher or lower support percentages for Harris. By including pollster as a predictor, we aim to control for this source of variability, helping the model focus on underlying trends rather than discrepancies introduced by polling differences.

@@

We define our model as:

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \beta_0 + \beta_1 \times \mbox{State}_i + \beta_2 \times \mbox{Pollster}_i + \beta_3 \times \mbox{Days since first poll}_i\\
\beta_0 &\sim \mbox{Normal}(0, 2.5) \\
\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
\beta_2 &\sim \mbox{Normal}(0, 2.5) \\
\beta_3 &\sim \mbox{Exponential}(1)
\end{align}
```

We used the `stan_glmer` function from `rstanarm` package to create a Bayesian regression model with a Normal distribution. The dependent variable in the proportion of respondent who support Kamala Harris, and our model aims to predict Harris' support based on several important factors, modeled by:

# Define Model
model <- cbind(num_harris, sample_size - num_harris) ~ (1 | state) + (1 | pollster) + (1 | end_date_num)

priors <- normal(0, 2.5, autoscale = TRUE)

bayesian_model <- stan_glmer(
  formula = model,
  data = harrisdata,
  family = binomial(link = "logit"),
  prior = priors,
  prior_intercept = priors,
  # weights = harrisdata$numeric_grade,
  seed = 123,
  cores = 4,
  adapt_delta = 0.95)
```

where:

- $y_i$ is the dependent variable, represneting the proportion of respondents who support Harris
- $\beta_0$ is the intercept term, representing the expected proportion of $y_i$ when all other predictors are set to zero.
- $\beta_1$ corresponds to the `state` choosing one of seven states,
- $\beta_2$ corresponds to the `pollster`,
- $\beta_3$ is the value representing number of days since the first poll.

All variables follow the normal distribution with a mean of 0 and a standard deviation of 2.5.

@@

# Plot checks for Model
pp_check(bayesian_model)
plot(bayesian_model, pars = "(Intercept)", prob = 0.95)
modelsummary::modelsummary(
  list(
    "First model" = bayesian_model
  ),
  statistic = "mad",
  fmt = 2
)
```

harrisdata <- harrisdata %>% drop_na()
expected_probs <- posterior_epred(bayesian_model, newdata = harrisdata)
median_probs <- apply(expected_probs, 2, median)
harrisdata <- harrisdata %>%
  mutate(median_prob = median_probs)

ggplot(harrisdata, aes(x = end_date_num, y = median_prob, color = state)) +
  geom_line(alpha = 0.5) +  # Plot raw data with some transparency to show noise
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs", k = 10), se = FALSE) +  # Smoother with flexible spline
  labs(
    title = "Predicted Probability of Harris Outcome Over Time by State",
    x = "Days Since First Poll (end_date_num)",
    y = "Predicted Probability"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ state, scales = "free_y")

ggplot(harrisdata, aes(x = end_date_num, y = median_prob, color = state)) +
  geom_line(alpha = 0.5) +  # Plot raw data with some transparency
  geom_smooth(method = "loess", span = 0.3, se = FALSE) +  # Add a less smoothed trend line
  labs(
    title = "Predicted Probability of Harris Outcome Over Time by State",
    x = "Days Since First Poll (end_date_num)",
    y = "Predicted Probability"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ state, scales = "free_y")

```
```{r}
expected_probs <- posterior_epred(bayesian_model, newdata = harrisdata)

# Calculate the mean predicted probability across all observations (overall predicted support percentage)
overall_predicted_support <- mean(rowMeans(expected_probs)) * 100
overall_predicted_support

```{r}
expected_probs <- posterior_epred(bayesian_model, newdata = harrisdata)

@@

# Print the table
predicted_support_table
```

@@

## Model set-up

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

What do we expect...
We expect a predictions in the high 40% based on our current data.

@@

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

@@

# Appendix {.unnumbered}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

@@

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: false
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

# Appendix 2
Here we will be talking about how we would conduct a $100,000 surevey to gather data about this upcoming election to ensure there is minimal error in the data we are collecting and, our data represents the facts we want them to represent. 
Out of the \$100,000 we will allocate \$15000 for the necessary development and administration of the data. This means we will be spending this money to create the survey, and have a infrastructure in place to hold the large amount of data as well as cover any security fees to keep this data private and safe. Then we allocate $50000 to advertise the survey. We will need a large sample so we will be spending most of our budget for this. We will have a different urls for each advertisement we have so that we can incorporate this in our data to see which demographic is accessing the survey through which platform. The platforms to advertise this is through spotify, facebook, instagram, and some news networks. If possible we will try to use this money to get it endorsed by branches of government to show our reliability. Reliability is also what citizens respond to so this will get a lot of respondants. We will spend \$25,000 for modeling our data as they tend to be expensive with data this size. And the rest of the \$15,000 will be leftover cost for anything that we don't foresee. If there is any leftover we can add a survey participation price such as having a free 3 month trial for the platforms we mentioned above (that is if they have a subscription based membership).

@@

>>>>

## Measurement/ Data Visualization {#sec-graphs}

@@

```{r, fig.height= 2.5}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportstate
#| fig-cap: "Distribution of Support Percentage by State"

@@

harrisdata <- harrisdata %>%
  mutate(end_date_num = as.numeric(end_date - min(end_date)),
        state = factor(state))

@@

combined_data <- harrisdata %>%
  inner_join(trumpdata, by = c("state", "pollster", "sample_size", "end_date")) %>%
  mutate(
    harris_percentage = (num_harris / sample_size) * 100,
    trump_percentage = (num_trump / sample_size) * 100)

@@

plot_data <- combined_data %>%
  pivot_longer(cols = c(harris_percentage, trump_percentage),
               names_to = "candidate",
               values_to = "support_percentage") %>%
  mutate(candidate = ifelse(candidate == "harris_percentage", "Harris", "Trump"))

ggplot(plot_data, aes(x = state, y = support_percentage, fill = candidate)) +
  geom_bar(stat = "identity", position = position_dodge(width = 0.9)) +
  labs(,
    x = "State",
    y = "Support Percentage"
  ) +
  scale_fill_manual(values = c("Harris" = "deepskyblue2", "Trump" = "tomato1"), name = "Candidate") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 30, hjust = 1, vjust = 1, size = 8))
```

@@

```{r, fig.height= 3.5, fig.width= 6.5}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportharris
#| fig-cap:  "Support Percentage for Harris by State"

@@

ggplot(harrisdata, aes(x = state, y = pct)) +
  geom_boxplot(aes(fill = state), alpha = 0.6, outlier.shape = NA) + 
  geom_jitter(aes(color = state), width = 0.2, alpha = 0.4) + 
  labs(
    x = "State",
    y = "Support Percentage") +
  theme_minimal() +
  theme(legend.position = "none") 
```

@@

```{r, fig.width= 6, fig.height= 2.5}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportWP
#| fig-cap:  "Support Percentage for Harris by State since Harris declared as Candidate for Wisconsin and Pennsylvania"

subset1 <- harrisdata %>% filter(state %in% c("Wisconsin", "Pennsylvania"))

ggplot(subset1, aes(x = end_date, y = pct, color = state)) +
  geom_point() +
  geom_smooth(se = TRUE) +
  facet_wrap(~ state, scales = "free_y") +
  labs(y = "Harris Percent", x = "Date") +
  theme_minimal() +
    scale_x_date(
    date_breaks = "1 month",           
    date_minor_breaks = "1 week",     
    date_labels = "%b %d" ) +
   theme(legend.position = "none")

In @fig-supportWP, Pennsylvania and Wisconsin display distinct trends. In Pennsylvania, support for Harris has been relatively consistent since early September, stabilizing around 48.5%. In contrast, Wisconsin shows a peak in support in mid-September, followed by a gradual decline that stabilizes in October. These observations suggest that while Pennsylvania remains a consistent stronghold for Harris, Wisconsin’s voter sentiment may be more susceptible to fluctuations.

```{r, fig.width= 6, fig.height= 2.5}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportAM
#| fig-cap:  "Support Percentage for Harris by State since Harris declared as Candidate"

@@

```{r, fig.width= 7, fig.height= 2.5}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportGNN
#| fig-cap:  "Support Percentage for Harris by State since Harris declared as Candidate"

@@

# Plot the first subset
ggplot(subset3, aes(x = end_date, y = pct, color = state)) +
  geom_point() +
  geom_smooth(se = TRUE) +
  facet_wrap(~ state, scales = "free_y") +
  labs(y = "Harris Percent", x = "Date") +
  theme_minimal() +
        scale_x_date(
    date_breaks = "1 month",
    date_minor_breaks = "1 week",
    date_labels = "%b %d" 
  ) +
   theme(legend.position = "none")
```

In @fig-supportGNN, we analyze Georgia, Nevada, and North Carolina. Nevada demonstrates the highest variability in Harris's support, which could reflect the state’s dynamic political response to recent campaign efforts. Georgia shows a steady upward trend, indicating growing support for Harris, while North Carolina reveals a slight decline since October, suggesting a possible shift in voter support.

```{r, fig.width= 5, fig.height= 2.5}
#| echo: false
#| warning: false
#| message: false
#| label: fig-supportpollsters
#| fig-cap: "Variation in Harris's Support Percentage Across Pollsters Over Time"

@@

ggplot() +
  # Draw a line for each pollster from first to last poll
  geom_point(data = harrisdata %>% group_by(pollster) %>% filter(n() > 1), 
            aes(x = end_date_num, y = pct, group = pollster, color = pollster), 
            alpha = 0.1) +
  # Draw points for each poll (including those with only one poll)
  geom_point(data = harrisdata, aes(x = end_date_num, y = pct, color = pollster), 
             size = 0.5, alpha = 0.3) +
  # Add the median line with ribbon for variability
  geom_line(data = pollster_summary, aes(x = end_date_num, y = median_support), 
            color = "royalblue", size = 1) +
  geom_ribbon(data = pollster_summary, aes(x = end_date_num, ymin = lower_quartile, ymax = upper_quartile), 
              fill = "lightblue", alpha = 0.2) +
  labs(
    x = "Days Since Declaration",
    y = "Support Percentage"
  ) +
  theme_minimal() +
  theme(legend.position = "none")

In @fig-supportpollsters, we examine the impact of pollster variability on Harris's support percentage over time. This visualization introduces the variable pollster, highlighting the differences in polling results that arise from varying methodologies. The chart reveals considerable fluctuations and occasional outliers in Harris' support, likely due to the distinct approaches each pollster employs in sampling and weighting responses.

@@

@@

1. **State**: Since support for candidates can vary significantly across different states due to regional demographics, political history, and local issues, the state variable allows us to capture these geographical differences. As shown in the earlier visualizations, some states demonstrate consistently higher or lower support for Harris, emphasizing the importance of including state-level distinctions in our analysis.

2. **Days Since Declaration**: Representing the number of days since Harris declared her candidacy, this temporal variable helps us capture shifts in voter sentiment over time. Our analysis reveals several critical points where support trends noticeably change, such as the upward or downward shifts in mid-September. This predictor allows the model to account for these temporal patterns and track how Harris’s support evolves as the campaign progresses.

3. **Pollster**: Given that different pollsters employ varied methodologies, sampling techniques, and weighting schemes, the pollster variable captures the potential variability introduced by each polling organization. As illustrated in @fig-supportpollsters, the results can vary considerably depending on the pollster, with some reporting notably higher or lower support percentages for Harris. By including pollster as a predictor, we aim to control for this source of variability, helping the model focus on underlying trends rather than discrepancies introduced by polling differences.

@@

## Model Step- Up

We used the `stan_glmer` function from the `rstanarm` package to create a Bayesian regression model with a binomial family and logit link. This model is designed to predict the proportion of respondents who support Kamala Harris based on several key factors.

The model specification is as follows:

```{=tex}
\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \beta_0 + \beta_1 \times \mbox{State}_i + \beta_2 \times \mbox{Pollster}_i + \beta_3 \times \mbox{Days since first poll}_i\\
\beta_0 &\sim \mbox{Normal}(0, 2.5) \\
\beta_1 &\sim \mbox{Normal}(0, 2.5) \\
\beta_2 &\sim \mbox{Normal}(0, 2.5) \\
\beta_3 &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}
```

The outcome variable in this model is the proportion of respondents who support Harris in each poll, represented as $y_i$. This binomial outcome (successes out of the total sample size) is modeled as a function of several predictor variables that account for differences by state, pollster, and time.

- $y_i$ is the dependent variable, representing the proportion of respondents who support Harris.
- $\beta_0$: The intercept term, representing the expected proportion of $y_i$ when all other predictors are set to zero.
- **State** ($\beta_1$): Categorical variable that accounts for differences in support across seven key swing states.
- **Pollster** ($\beta_2$): Categorical variable capturing variability introduced by the polling organization.
- **Days since first poll** ($\beta_3$): Numeric variable representing the number of days since Harris declared her candidacy.

Each coefficient $beta$ follows the normal distribution with a mean of 0 and a standard deviation of 2.5, providing some regularization while allowing for a range of possible effects. The standard deviation $\sigma$ is given an Exponential(1) prior, which constrains it to positive values and provides a realistic expectation of variability around the mean 
Each predictor captures a unique dimension of voter sentiment:

- **State** accounts for regional differences in support due to factors like demographics and political history.
- **Pollster** adjusts for methodological variations in polling, which we observed to influence support percentages.
- **Days Since Declaration** captures temporal trends, allowing the model to incorporate fluctuations in voter sentiment over the campaign period.

By combining these predictors, the model aims to forecast Harris’s support by isolating genuine trends from random variability.

Based on the data overview in @sec-graphs, we observe that Harris’s support varies across key swing states, and we expect these regional differences to influence our model's predictions. The state variable is anticipated to capture these geographic variations, with states like Arizona, Michigan, Georgia, and Pennsylvania showing relatively consistent high levels of support for Harris. In contrast, Nevada, North Carolina, and Wisconsin exhibit a declining trend in support. We expect the intercept to be around 50%, as this reflects the average level of support observed across all states and pollsters.

A model validation is included in `scripts/05-exploratory_data_analysis.R`, and a Posterior Predictive Check and summary statistics for the model are included in @sec-checks.

## Model Results

The model predicts an average support percentage of approximately 47.33% for Kamala Harris across the selected states. This percentage reflects the central tendency of predicted support within the dataset, factoring in the influence of state, pollster, and the number of days since the first poll.

The results indicate variations in predicted support across states. For instance, Pennsylvania and Wisconsin show the highest average predicted support percentages (48.02% and 48.38%, respectively), while states like Nevada and Arizona display slightly lower support.

In states like Arizona, Georgia, Michigan, and North Carolina, the model predicts a steady increase in support for Harris over time, as shown in @fig-modelGAWM.
In states such as Nevada, Pennsylvania, and Wisconsin, the model predicts a decline in support over time, as seen in @fig-modelNPW.

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-modelGAWM
#| fig-cap: "Poll predictions of Arizona, Geogria, Michigan, North Carolina"

bay_model <-
  readRDS(file = here::here("models/bay_model.rds"))

harrisdata_clean <- harrisdata %>% drop_na()

harrisdata <- harrisdata %>% drop_na()
expected_probs <- posterior_epred(bay_model, newdata = harrisdata)
median_probs <- apply(expected_probs, 2, median)
harrisdata <- harrisdata %>%
  mutate(median_prob = median_probs)

subset_up <- harrisdata %>% filter(state %in% c("Arizona", "Georgia", "Michigan", "North Carolina"))

ggplot(subset_up, aes(x = end_date_num, y = median_prob, color = state)) +
  geom_line(alpha = 0.5) +  
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs", k = 10), se = FALSE) +
  labs(
    x = "Days Since First Poll",
    y = "Predicted Probability"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ state) +
  theme(legend.position = "none")

```
In @fig-modelNPW, we see states of Nevada, Pennsylvania and Wisconsin have a singular declining trend.

```{r}
#| echo: false
#| warning: false
#| message: false
#| label: fig-modelNPW
#| fig-cap: "Poll predictions of Nevada, Pennsylvania, Wisconsin"

subset_down <- harrisdata %>% filter(state %in% c("Nevada", "Pennsylvania", "Wisconsin"))

ggplot(subset_down, aes(x = end_date_num, y = median_prob, color = state)) +
  geom_line(alpha = 0.5) +
  geom_smooth(method = "gam", formula = y ~ s(x, bs = "cs", k = 10), se = FALSE) + 
  labs(
    x = "Days Since First Poll",
    y = "Predicted Probability"
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  facet_wrap(~ state, ncol = 2) +
    theme(legend.position = "none")

CONFIDENCE INTERVAL TABLE ??

@@

expected_probs <- posterior_epred(bay_model, newdata = harrisdata)

@@

# Print the table
predicted_support_table
```
```{r}

@@

@@

@@

@@

# Appendix 2

Here we will be talking about how we would conduct a $100,000 surevey to gather data about this upcoming election to ensure there is minimal error in the data we are collecting and, our data represents the facts we want them to represent. 
Out of the \$100,000 we will allocate \$15000 for the necessary development and administration of the data. This means we will be spending this money to create the survey, and have a infrastructure in place to hold the large amount of data as well as cover any security fees to keep this data private and safe. Then we allocate $50000 to advertise the survey. We will need a large sample so we will be spending most of our budget for this. We will have a different urls for each advertisement we have so that we can incorporate this in our data to see which demographic is accessing the survey through which platform. The platforms to advertise this is through spotify, facebook, instagram, and some news networks. If possible we will try to use this money to get it endorsed by branches of government to show our reliability. Reliability is also what citizens respond to so this will get a lot of respondents. We will spend \$25,000 for modeling our data as they tend to be expensive with data this size. And the rest of the \$15,000 will be leftover cost for anything that we don't foresee. If there is any leftover we can add a survey participation price such as having a free 3 month trial for the platforms we mentioned above (that is if they have a subscription based membership).

@@

# Appendix 3 - checks and summary stats {#sec-checks}

# Plot checks for Model
pp_check(bay_model)
plot(bay_model, pars = "(Intercept)", prob = 0.95)
modelsummary::modelsummary(
  list(
    "First model" = bay_model
  ),
  statistic = "mad",
  fmt = 2
)
```
